Trends of downward SDR in Thessaloniki

### 2023-05-09 Article.Rmd
Commit 2023-05-10 01:17

```{r trendALL, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for all sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

>>>>

```{r trendALL, echo=F, fig.cap="Anomaly (\\%) of the daily Global radiation relative to climatogical values for 1993 - 2022. The straight black line shows the lond term trend for All-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

## Trends by SZA
